\chapter{Introduction}

\section{About this document}

This manual provides instructions for the installation and usage of the
productline management system Kobold.

\section{Background information}

Short time-to-market cycles, high product quality und low costs are the 
key factors for success in the field of software engineering. These incompatible 
goals can be reached through systematic reuse throughout the development of
software. \par

The gist of the productline approach is to systematically gather the differences
and commonalities of different products and to explicitly picture these aspects
in form of a software architecture. This effects all steps in the development
process and in the design and strategy of products.\par

In order to establish an efficient productline development in the field of
software engineering, you have to put this product strategy rigorously into
practice.\par

The ideal goal of a well-configured productline is to create a product with a
simple combination of core assets which are customized for the product. Therefore 
a productline is ideally configured if the productline architecture is sufficiently
specified for all possible products. This is the task of a product(line) engineer.
He specifies the architecture by defining core assets and their main relations 
(scoping and domain engineering). If a new product is to be added to the productline 
(application engineering), it has to follow this architecture. In order to achieve
this existing variants of core assets are combined with new variants und transferred
to the product engineer who takes responsibility for this product. He has to make
sure that the development of the product does not interfere with the architecture
of the productline.\par

In this hierarchy it is important that procedures are performed according to fixed
rules. For example, if an existing variant of a core asset is already used in
a product, it mustn't be changed by the product engineer. Changes are only
allowed by the responsible core asset developer. He has to decide whether the
changes are useful since his core asset is also used in other products. If he declines
the changes, the product engineer has to develop a product-specific variant of the
core asset. This process is very complex because several people take part in 
the decision. In order to enforce a productline rigorously these operations must
be specified. \par

Kobold supports the development of productlines, simplifies the configuration
management, the communication and the development and helps to model 
operations



\section{Structure of this document}
This user manual will help you to install the Kobold system and to
determine the technical conditions. \par
The description of the usage is divided in three parts. The first part provides descriptions of each window and
each menu item. 
\par
The second part is a short tutorial through which you can start working with Kobold right away.\par
The third part is a list of the interfaces you need to implement your own workflow
rules (for more information see chapter 4).